\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{parskip}

\hypersetup{colorlinks=true, urlcolor=blue}
\pagestyle{empty}

\begin{document}

\begin{flushleft}
\textbf{Jo\~{a}o Roberto Lawall Soares}\\
blsoaresdev@gmail.com\\
+55 51 991363373\\
\href{https://github.com/Dnreikronos}{github.com/Dnreikronos} \quad \href{https://www.linkedin.com/in/blsoaresdev/}{linkedin.com/in/blsoaresdev}
\end{flushleft}

\vspace{12pt}

\begin{flushleft}
April 25, 2026\\
\vspace{6pt}
OneSignal\\
Senior Software Engineer -- Analytics Team
\end{flushleft}

\vspace{12pt}

Hi,

I'm applying for the Senior Software Engineer position on OneSignal's Analytics team. I've spent 6+ years building backend services in Go and Rust, and the combination of your scale (1.3T messages/year), your stack (Rust, Go, Kafka, Kubernetes), and the problem space -- turning messaging data into something customers can act on -- is exactly where I want to be working.

At my current role, I work on a system that processes 140M+ monthly transactions through Apache Kafka. I tracked down a concurrency bug in the consumer pipeline that was causing duplicate invoices and fixed it with mutex-based synchronization. Zero downtime, no data loss. I also migrated our database layer from Oracle to PostgreSQL, which involved rewriting query plans and adding indexes that cut our slowest queries by over a minute. These are the kinds of problems I like: high-throughput distributed systems where getting the details wrong costs real money.

On the Rust side, I contribute to the Zed code editor (70k+ GitHub stars). I've had 19 PRs merged across 15+ subsystems -- fixing a deadlock in the rendering framework, debugging terminal layout issues caused by floating-point precision, reworking selection logic across 11 files. It's given me a solid feel for large Rust codebases and the kind of careful systems thinking that comes with them.

I use AI tooling heavily in my daily work. I built Auto-Issue, a Go application that takes GitHub issues, routes them to AI agents (Claude Code, Codex, or Gemini), and produces PRs with self-reviewed code. The backend handles orchestration, work queues, concurrency limiting, and git worktree isolation per issue. I also use Claude Code, Cursor, and Codex throughout my regular development workflow for code generation, reviews, and testing.

I've deployed and monitored services on Docker and Kubernetes, participated in on-call rotations, and written technical design documents for new features. I've worked with PostgreSQL and MongoDB extensively, including query optimization that brought an 85\% improvement on MongoDB aggregation pipelines. I design RESTful APIs and gRPC endpoints, and I follow clean architecture principles without being rigid about it.

Happy to talk more about how my background fits what you're building on the Analytics team.

\vspace{12pt}

Best regards,\\
Jo\~{a}o Roberto Lawall Soares

\end{document}
