\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{array}

\definecolor{headercolor}{RGB}{51, 51, 51}
\definecolor{subtitlecolor}{RGB}{102, 102, 102}
\definecolor{accentcolor}{RGB}{0, 102, 204}
\definecolor{lightgray}{RGB}{245, 245, 245}

\hypersetup{colorlinks=true, linkcolor=accentcolor, urlcolor=accentcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, nosep, itemsep=0.5pt, label=\textbullet}

\titleformat{\section}{\large\bfseries\centering}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\newcommand{\experienceheader}[4]{
    \textbf{\color{subtitlecolor}#1} \hfill #2\\
    \textbf{#3} \hfill \textit{#4}\\
}

\newcommand{\achievementbox}[3]{
    \begin{minipage}[t]{0.3\textwidth}
        \centering
        \colorbox{lightgray}{\makebox[0.9\textwidth][c]{
            \begin{minipage}{0.85\textwidth}
                \centering
                \vspace{3pt}
                #1\ \textbf{\footnotesize #2}\\[1pt]
                {\footnotesize #3}
                \vspace{3pt}
            \end{minipage}
        }}
    \end{minipage}
}

\begin{document}

\begin{center}
    {\LARGE\bfseries\color{headercolor} João Roberto Lawall Soares}\\[3pt]
    {\large\color{subtitlecolor} Software Engineer | Backend Architecture | Cloud \& Web3}\\[4pt]
    {\footnotesize +55 51 991363373 \quad • \quad blsoaresdev@gmail.com \quad • \quad \href{https://www.linkedin.com/in/blsoaresdev/}{LinkedIn} \quad • \quad \href{https://github.com/Dnreikronos}{GitHub} \quad • \quad Brazil (UTC-3) | Remote | US/EU Time Zone Overlap}
\end{center}

\section{Summary}
{\footnotesize Backend Engineer with 6+ years building production systems in Golang. Focused on concurrency, distributed architectures, microservices, and observability on Kubernetes. Fixed a critical Kafka bug in a system processing 140M+ monthly transactions, cut query times by up to 85\%, and helped ship the company's first AI/RAG feature. Contribute to the Zed code editor in Rust (70k+ GitHub stars) and build smart contracts in Solidity and Solana.}

\section{Key Achievements}

\vspace{2pt}
\noindent
\achievementbox{\faDiamond}{Concurrency \& Scale}{100\% resolution of critical Kafka bug affecting 140M+ monthly transactions with zero downtime.}
\hfill
\achievementbox{\faDiamond}{Performance}{Achieved 85\% query improvement (30s reduction) on MongoDB operations.}
\hfill
\achievementbox{\faDiamond}{Migration Scale}{Migrated invoicing stack from Oracle/Java to PostgreSQL/Golang at Brazil's largest pharmaceutical retailer, eliminating legacy licensing costs.}

\section{Experience}

\vspace{2pt}
\experienceheader{Platform Builders}{Brazil (Remote)}{Senior Golang Engineer}{Aug 2025 - Present}
\textbf{\footnotesize Full-time | RD Sa\'{u}de - Brazil's largest pharmaceutical retailer}
\begin{itemize}
    \item {\footnotesize Fixed a concurrency bug in the invoicing pipeline that caused fiscal compliance failures across 140M+ monthly transactions. Used mutex-based synchronization to eliminate the race condition.}
    \item {\footnotesize Hardened Apache Kafka consumers with lock-based deduplication, reaching 99.99\% idempotency and stopping duplicate invoice generation entirely.}
    \item {\footnotesize Migrated the database layer from Oracle to PostgreSQL. Rewrote execution plans and added targeted indexes, cutting query times by over 1 minute on the slowest queries.}
    \item {\footnotesize Eliminated Oracle Database licensing fees and cut JVM memory footprint by migrating the invoicing stack from Java/Oracle to Golang/PostgreSQL, saving roughly \$10k in licensing and compute costs.}
    \item {\footnotesize Maintained 98\%+ unit test coverage across 60+ Golang microservices, catching regressions before they reached the invoicing pipeline.}
    \item {\footnotesize Helped roll out Datadog Orchestrion auto-instrumentation across 60+ Golang microservices, giving DevOps and engineers full request tracing and runtime visibility into production behavior.}
    \item {\footnotesize Refactored goroutine lifecycle and pool management across backend services, reducing request latency by 40\%.}
    \item {\footnotesize Helped build the company's first AI feature: a Retrieval-Augmented Generation (RAG) system letting users query business rules and endpoint/screen behavior in natural language.}
    \item {\footnotesize Mentored 5 developers on Go concurrency patterns and architecture. Team velocity went up 30\% over the following quarter.}
    \item {\footnotesize Tech Stack: Golang, Apache Kafka, PostgreSQL, Docker, Kubernetes, ArgoCD, Datadog, OCI (Oracle Cloud), REST API, Microservices.}
\end{itemize}

\vspace{2pt}
\experienceheader{Borderless Coding}{USA (Remote)}{Web3 Technical Mentor \& Ambassador}{Sep 2025 - Present}
\textbf{\footnotesize Part-time}
\begin{itemize}
    \item {\footnotesize Mentored 60+ professionals on Solidity smart contracts and blockchain architecture. 95\% satisfaction rate across cohorts.}
    \item {\footnotesize Ran 20+ live workshops on smart contract development using Foundry, Hardhat, and Remix IDE. 90\% of participants completed the full course.}
    \item {\footnotesize Grew the technical community by 200\% with hands-on content covering Ethereum, Solana, and DeFi protocols.}
\end{itemize}

\vspace{2pt}
\experienceheader{Docile Alimentos LTDA}{Brazil (Remote)}{Senior Backend Engineer}{Jan 2020 - Aug 2025}
\textbf{\footnotesize Full-time | B2C food manufacturer (\textasciitilde R\$1B annual revenue)}
\begin{itemize}
    \item {\footnotesize Migrated a Java/JSF monolith to Spring Boot microservices, cutting new-feature delivery time by \textasciitilde3 days per task and resolving long-standing reliability issues from the legacy system.}
    \item {\footnotesize Built a MongoDB-backed application for the Accounting team to auto-validate fiscal documents (NF-e) against user-defined rule sets. Owned the database and indexing strategy, cutting query times by up to 85\% (over 1 minute reduction on the heaviest aggregations).}
    \item {\footnotesize Built an internal platform used directly by Commercial and Marketing teams to manage promotional campaigns for B2C clients, replacing manual spreadsheet workflows.}
    \item {\footnotesize Built Golang backend services for data processing. Introduced concurrency patterns that increased throughput by 50\%.}
    \item {\footnotesize Built Python RPAs adopted by Financial, Commercial, Accounting, and Marketing teams, automating file imports and recurring workflows. Saved up to a full workday per task and \textasciitilde15 hours/week on imports alone.}
    \item {\footnotesize Rewrote indexes on 20+ PostgreSQL queries, averaging 45\% faster execution times.}
    \item {\footnotesize Onboarded new engineers on application architecture, database design, SQL query optimization, production data analysis, and engineering environment setup.}
    \item {\footnotesize Tech Stack: Golang, Java, Spring Boot, NestJS, Python, React, Angular, MongoDB, PostgreSQL, SQL Server, Docker, Linux, RPA, REST API, Microservices.}
\end{itemize}

\section{Technical Skills}

\vspace{2pt}
\noindent{\footnotesize
\textbf{Languages:} Go (Golang), Java, TypeScript, JavaScript, Rust (Solana), Solidity, SQL, Bash\\
\textbf{Backend:} Spring Boot, Spring Framework, JSF, NestJS, Express.js, REST API, GraphQL, gRPC, Microservices\\
\textbf{Frontend:} React, Angular, Next.js, TypeScript, JavaScript, HTML5, CSS3\\
\textbf{Cloud:} AWS (EC2, S3, RDS, Lambda), Oracle Cloud Infrastructure (OCI), Docker, Kubernetes, CI/CD, Linux\\
\textbf{Databases:} PostgreSQL, MongoDB, Redis, Elasticsearch, MySQL, SQL Server, Query Optimization\\
\textbf{Messaging:} Apache Kafka, RabbitMQ, Amazon SQS, Event-Driven Architecture\\
\textbf{Architecture:} Microservices, Clean Architecture, SOLID, Design Patterns, DDD, TDD, Distributed Systems Design, System Architecture\\
\textbf{DevOps:} Docker, ArgoCD, CI/CD Pipelines, Datadog, Grafana, ELK Stack, Prometheus, Application Performance Monitoring\\
\textbf{Web3:} Solidity, Solana (Rust), Smart Contracts, Ethereum, DeFi, NFTs, MetaMask, Phantom Wallet, ZK Proofs, NEAR Protocol\\
\textbf{Tools:} Git, GitHub, GitLab, Jira, Agile/Scrum, RPA, Jaspersoft Reports, Salesforce CRM, Cursor, Claude
}

\section{Open Source Contributions}

\vspace{2pt}
\noindent\textbf{\footnotesize Zed Editor} • {\footnotesize\href{https://github.com/zed-industries/zed}{GitHub (70k+ Stars)} — Rust}\\
{\footnotesize Contributor to Zed, a code editor written in Rust. 53 PRs submitted (19 merged) across 15+ subsystems, totaling 6,800+ lines:}
\begin{itemize}
    \item {\footnotesize Found and fixed a macOS deadlock in the GPUI rendering framework where re-entrant key status changes froze the UI. (\href{https://github.com/zed-industries/zed/pull/51035}{\#51035} -- Merged)}
    \item {\footnotesize Reworked picker selection logic across 11 files so non-selectable entries can no longer confirm unintended actions in the command palette. (\href{https://github.com/zed-industries/zed/pull/50705}{\#50705} -- Merged, +185/-51)}
    \item {\footnotesize Fixed \texttt{formatter: "auto"} so it skips language servers that cannot actually format, instead of failing silently. (\href{https://github.com/zed-industries/zed/pull/50661}{\#50661} -- Merged)}
    \item {\footnotesize Stopped the agent panel from stealing focus away from modals on workspace restore, which was breaking keyboard shortcuts. (\href{https://github.com/zed-industries/zed/pull/50511}{\#50511} -- Merged, +116/-62)}
    \item {\footnotesize Fixed SVG renderer not rendering text when system fonts are unavailable in GPUI. (\href{https://github.com/zed-industries/zed/pull/51623}{\#51623} -- Merged, +120/-7)}
    \item {\footnotesize Fixed visible escape characters in LSP diagnostic messages rendered via markdown. (\href{https://github.com/zed-industries/zed/pull/51766}{\#51766} -- Merged, +195/-27)}
    \item {\footnotesize Fixed deleted files persisting in project search results. (\href{https://github.com/zed-industries/zed/pull/50551}{\#50551} -- Merged, +175/-18)}
    \item {\footnotesize Improved code folding to include closing delimiter on same line. (\href{https://github.com/zed-industries/zed/pull/50090}{\#50090} -- Merged, +234/-26)}
    \item {\footnotesize Fixed semantic tokens not appearing when opening buffer from multibuffer, a core editor feature for accurate syntax highlighting. (\href{https://github.com/zed-industries/zed/pull/53712}{\#53712} -- Merged)}
    \item {\footnotesize Debugged and fixed terminal rendering missing the first line due to floating-point tolerance in the layout calculation. (\href{https://github.com/zed-industries/zed/pull/52111}{\#52111} -- Merged)}
    \item {\footnotesize Reset terminal cursor blink on text send and keystroke actions to prevent visual inconsistency. (\href{https://github.com/zed-industries/zed/pull/53171}{\#53171} -- Merged)}
    \item {\footnotesize Fixed git panel context menu jitter, improving UX consistency during rapid interactions. (\href{https://github.com/zed-industries/zed/pull/52217}{\#52217} -- Merged)}
    \item {\footnotesize Also contributed to GPUI (font fallback, drag states), DAP debugger, theme selector, markdown rendering, and platform-specific fixes on macOS and Linux/X11. (\href{https://github.com/zed-industries/zed/pulls?q=author\%3ADnreikronos}{View all PRs})}
    \item {\footnotesize 5 PRs (all merged) to the OCaml extension: added Dune package management support, MLX file support, LSP argument forwarding, and project root detection. (\href{https://github.com/zed-extensions/ocaml/pulls?q=author\%3ADnreikronos}{View all PRs})}
\end{itemize}

\section{Projects}

\vspace{2pt}
\noindent\textbf{\footnotesize DarkPool-Exchange | ZK Dark Pool DEX with Batch Auctions} • {\footnotesize\href{https://github.com/Dnreikronos/DarkPool-Exchange}{GitHub}}\\
{\footnotesize DEX where orders stay private until settlement. Traders encrypt orders to the operator and the engine matches them in periodic batch auctions (every 5 seconds by default) with a clearing price per round. Built the Rust and Web3 layer: halo2 / arkworks circuits proving order validity, client-side proof generation in Rust (WASM + native CLI), the proof aggregator that batches individual proofs into one on-chain check, and integration with the Solidity verifier and settlement contract. Order size and price surface only after the round closes, cutting front-running and MEV exposure.}

\vspace{2pt}
\noindent\textbf{\footnotesize zkSettle | ZK Compliance Infrastructure for Solana Stablecoins} • {\footnotesize\href{https://github.com/yuribodo/zksettle}{GitHub}}\\
{\footnotesize Solana compliance layer for stablecoin fintechs. Proves travel-rule and sanctions conformance without putting user PII on-chain. Built the Rust and Web3 side: an Anchor program with a Token-2022 Transfer Hook that verifies Groth16 proofs (BN254) via Solana \texttt{alt\_bn128} syscalls in under 200K compute units, nullifier storage on Light Protocol state compression, and the off-chain Rust workspace (issuer service, OFAC sanctions updater with a Sparse Merkle Tree, Helius-webhook indexer that pins attestations to Arweave, axum API gateway). Proof generation runs in the user's browser via Noir + WASM, so no PII ever leaves the device.}

\vspace{2pt}
\noindent\textbf{\footnotesize Auto-Issue | Autonomous GitHub Issue Agent} • {\footnotesize\href{https://github.com/yuribodo/auto-issue}{GitHub}}\\
{\footnotesize Electron + Go app that takes a GitHub issue, sends it to an AI agent (Claude Code, OpenAI Codex, or Gemini), and produces a PR with self-reviewed code. Built the entire Go backend: multi-provider agent system that spawns CLI subprocesses with PTY streaming, an orchestrator with a work queue and concurrency limiter managing the issue lifecycle (backlog, developing, code review, human review, done), git worktree isolation per issue, SSE real-time output to the frontend, and a REST API with 15+ endpoints. Backend uses GORM with PostgreSQL for persistence.}

\vspace{2pt}
\noindent\textbf{\footnotesize Crypto-Tip | Decentralized Tipping Platform} • {\footnotesize\href{https://github.com/Dnreikronos/crypto-tip}{GitHub (34 Stars)}}\\
{\footnotesize Smart contracts in Solidity (Ethereum) and Rust (Solana) for open-source funding. Integrates MetaMask and Phantom wallets.}

\vspace{2pt}
\noindent\textbf{\footnotesize givemoney.fun | Web3 Streaming Donation Platform}\\
{\footnotesize Web3 app for Twitch/Kick/YouTube streamers to receive crypto donations. Solidity and Solana smart contracts with reentrancy guards.}

\vspace{2pt}
\noindent\textbf{\footnotesize Veste AI | AI-Powered Fashion Assistant} • {\footnotesize\href{https://github.com/Dnreikronos/HB02-2025_braindancers}{GitHub}}\\
{\footnotesize Golang backend that uses the Google Gemini API to analyze outfits. Built at a hackathon. REST API with cloud-based image processing.}

\vspace{2pt}
\noindent\textbf{\footnotesize Proof Of Learn | AI + Web3 Platform} • {\footnotesize\href{https://github.com/Dnreikronos/proof-of-learn}{GitHub (NearX \& ZKVerify Hackathon)}}\\
{\footnotesize Generates AI-powered learning roadmaps with on-chain incentives. Uses NEAR Protocol and Zero-Knowledge Proofs for NFT credential issuance.}

\vspace{2pt}
\noindent\textbf{\footnotesize Pattpay | Web3 Payment Gateway} • {\footnotesize\href{https://github.com/Dnreikronos/pattpay}{GitHub (Cypherpunk Hackathon)}}\\
{\footnotesize Subscription billing on Solana. Smart contracts handle recurring payments with sub-second finality using SPL tokens.}

\section{Education}

\vspace{2pt}
\noindent\textbf{\footnotesize Universidade do Vale do Taquari - Univates} \hfill {\footnotesize 2021 - 2025}\\
{\footnotesize Bachelor's Degree, Computer Science}

\section{Languages}

\vspace{2pt}
\begin{center}
{\footnotesize \textbf{English} - Proficient (Professional Working Proficiency) \quad\quad \textbf{Portuguese} - Native Speaker}
\end{center}

\end{document}
