\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{array}

\definecolor{headercolor}{RGB}{51, 51, 51}
\definecolor{subtitlecolor}{RGB}{102, 102, 102}
\definecolor{accentcolor}{RGB}{0, 102, 204}
\definecolor{lightgray}{RGB}{245, 245, 245}

\hypersetup{colorlinks=true, linkcolor=accentcolor, urlcolor=accentcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, nosep, itemsep=0.5pt, label=\textbullet}

\titleformat{\section}{\large\bfseries\centering}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{3pt}

\newcommand{\experienceheader}[4]{
    \textbf{\color{subtitlecolor}#1} \hfill #2\\
    \textbf{#3} \hfill \textit{#4}\\
}

\begin{document}

\begin{center}
    {\LARGE\bfseries\color{headercolor} Jo\~{a}o Roberto Lawall Soares}\\[3pt]
    {\large\color{subtitlecolor} Senior Software Engineer | Rust \& Golang | Backend Microservices at Scale}\\[4pt]
    {\footnotesize +55 51 991363373 \quad \textbullet \quad blsoaresdev@gmail.com \quad \textbullet \quad \href{https://www.linkedin.com/in/blsoaresdev/}{LinkedIn} \quad \textbullet \quad \href{https://github.com/Dnreikronos}{GitHub} \quad \textbullet \quad Lajeado, RS, Brazil (GMT-3)}
\end{center}

\section{Summary}
{\footnotesize Senior Software Engineer with 6+ years building backend microservices at scale in Golang and Rust. Fixed a critical Apache Kafka consumer bug in a system processing 140M+ monthly transactions and cut database query times by up to 85\%. Deploy and monitor services on Docker and Kubernetes. Design RESTful APIs and gRPC endpoints following clean software design principles. Use AI tooling daily (Claude Code, Cursor, Codex) for code generation, reviews, and automated testing. Contribute to the Zed code editor in Rust (70k+ GitHub stars), with 19 merged PRs.}

\section{Professional Experience}

\vspace{2pt}
\experienceheader{Platform Builders}{Brazil (Remote)}{Senior Software Engineer}{Aug 2025 - Present}
\textbf{\footnotesize Full-time | RD Sa\'{u}de - Brazil's largest pharmaceutical retailer}
\begin{itemize}
    \item {\footnotesize Fixed a concurrency bug in Apache Kafka consumers that caused failures across 140M+ monthly transactions. Used mutex-based synchronization to eliminate the race condition with zero downtime.}
    \item {\footnotesize Added idempotency locking to Kafka consumers, reaching 99.99\% deduplication and stopping duplicate processing across a distributed event streaming pipeline.}
    \item {\footnotesize Migrated database layer from Oracle to PostgreSQL. Rewrote execution plans and added targeted indexes, cutting query times by over 1 minute on the slowest queries.}
    \item {\footnotesize Shipped 15+ features in Golang with zero production incidents. Reworked goroutine management to reduce system latency by 40\%.}
    \item {\footnotesize Deployed and monitored microservices on Docker and Kubernetes. Participated in on-call rotation, resolving production issues and scaling services to meet traffic spikes.}
    \item {\footnotesize Wrote technical design documents for new features. Led peer code reviews and design spec reviews across the backend team.}
    \item {\footnotesize Mentored 5 developers on Go concurrency patterns. Team velocity went up 30\%.}
\end{itemize}

\vspace{2pt}
\experienceheader{Borderless Coding}{London Area, UK (Remote)}{Web3 Technical Mentor \& Ambassador}{Sep 2025 - Present}
\textbf{\footnotesize Part-time}
\begin{itemize}
    \item {\footnotesize Mentored 60+ professionals on Solidity smart contracts and Solana program development (Rust/Anchor). 95\% satisfaction rate across cohorts.}
    \item {\footnotesize Ran 20+ live workshops covering smart contract development using Foundry, Hardhat, and Anchor. 90\% completion rate.}
    \item {\footnotesize Grew technical community by 200\% with hands-on content covering Ethereum, Solana, and cross-chain patterns.}
\end{itemize}

\vspace{2pt}
\experienceheader{Docile Alimentos LTDA}{Lajeado, RS, Brazil (On-site)}{Backend Engineer}{Jan 2020 - Aug 2025}
\textbf{\footnotesize Full-time}
\begin{itemize}
    \item {\footnotesize Built Golang backend microservices for data processing. Introduced concurrency patterns that increased throughput by 50\%.}
    \item {\footnotesize Broke apart a Java monolith into Spring Boot microservices with RESTful APIs. Performance improved 40\%.}
    \item {\footnotesize Cut MongoDB query times by 85\% (30s faster) by reworking aggregation pipelines and adding targeted indexes after profiling slow endpoints.}
    \item {\footnotesize Rewrote indexes on 20+ PostgreSQL queries, averaging 45\% faster execution times.}
    \item {\footnotesize Owned RESTful APIs and gRPC endpoints used by internal tools and external integrations.}
    \item {\footnotesize Built continuous integration pipelines with Docker. Worked in Agile sprints with two-week releases.}
    \item {\footnotesize Automated file imports with RPA, cutting 15 hours/week of manual work (70\% reduction).}
    \item {\footnotesize Built frontend interfaces in React and Angular for internal tools and dashboards.}
\end{itemize}

\section{Open Source Contributions}

\vspace{2pt}
\noindent\textbf{\footnotesize Zed Editor} \textbullet{} {\footnotesize\href{https://github.com/zed-industries/zed}{GitHub (70k+ Stars)} --- Rust}\\
{\footnotesize Contributor to Zed, a code editor written in Rust. 53 PRs submitted (19 merged) across 15+ subsystems, totaling 5,000+ lines:}
\begin{itemize}
    \item {\footnotesize Found and fixed a macOS deadlock in the GPUI rendering framework where re-entrant key status changes froze the UI. (\href{https://github.com/zed-industries/zed/pull/51035}{\#51035} -- Merged)}
    \item {\footnotesize Reworked picker selection logic across 11 files so non-selectable entries can no longer confirm unintended actions. (\href{https://github.com/zed-industries/zed/pull/50705}{\#50705} -- Merged, +185/-51)}
    \item {\footnotesize Fixed SVG renderer not rendering text when system fonts are unavailable. (\href{https://github.com/zed-industries/zed/pull/51623}{\#51623} -- Merged, +120/-7)}
    \item {\footnotesize Debugged terminal rendering missing first line due to floating-point tolerance in layout calculation. (\href{https://github.com/zed-industries/zed/pull/52111}{\#52111} -- Merged)}
    \item {\footnotesize Fixed semantic tokens not appearing when opening buffer from multibuffer. (\href{https://github.com/zed-industries/zed/pull/53712}{\#53712} -- Merged)}
    \item {\footnotesize Also contributed to GPUI (font fallback, drag states), DAP debugger, LSP diagnostics, and platform-specific fixes on macOS and Linux/X11. (\href{https://github.com/zed-industries/zed/pulls?q=author\%3ADnreikronos}{View all PRs})}
\end{itemize}

\section{Projects}

\vspace{2pt}
\noindent\textbf{\footnotesize Auto-Issue | Autonomous GitHub Issue Agent} \textbullet{} {\footnotesize\href{https://github.com/yuribodo/auto-issue}{GitHub}}\\
{\footnotesize Electron + Go app that takes a GitHub issue, sends it to an AI agent (Claude Code, OpenAI Codex, or Gemini), and produces a PR with self-reviewed code. Built the entire Go backend: multi-provider agent system that spawns CLI subprocesses with PTY streaming, an orchestrator with a work queue and concurrency limiter managing the issue lifecycle (backlog, developing, code review, human review, done), git worktree isolation per issue, SSE real-time output to the frontend, and a REST API with 15+ endpoints. Backend uses GORM with PostgreSQL for persistence.}

\vspace{2pt}
\noindent\textbf{\footnotesize DarkPool-Exchange | ZK Dark Pool DEX with Batch Auctions} \textbullet{} {\footnotesize\href{https://github.com/Dnreikronos/DarkPool-Exchange}{GitHub}}\\
{\footnotesize DEX where orders stay private until settlement. Traders encrypt orders to the operator and the engine matches them in periodic batch auctions (every 5 seconds by default) with a clearing price per round. Built the Rust layer: halo2/arkworks circuits proving order validity, client-side proof generation in Rust (WASM + native CLI), the proof aggregator that batches individual proofs into one on-chain check, and integration with the Solidity verifier and settlement contract. Order size and price surface only after the round closes, cutting front-running and MEV exposure.}

\vspace{2pt}
\noindent\textbf{\footnotesize zkSettle | ZK Compliance Infrastructure for Solana Stablecoins} \textbullet{} {\footnotesize\href{https://github.com/yuribodo/zksettle}{GitHub}}\\
{\footnotesize Solana compliance layer for stablecoin fintechs. Proves travel-rule and sanctions conformance without putting user PII on-chain. Built the Rust side: an Anchor program with a Token-2022 Transfer Hook that verifies Groth16 proofs (BN254) via Solana \texttt{alt\_bn128} syscalls in under 200K compute units, nullifier storage on Light Protocol state compression, and the off-chain Rust workspace (issuer service, OFAC sanctions updater with a Sparse Merkle Tree, Helius-webhook indexer that pins attestations to Arweave, axum API gateway). Proof generation runs in the user's browser via Noir + WASM, so no PII ever leaves the device.}

\vspace{2pt}
\noindent\textbf{\footnotesize Crypto-Tip | Decentralized Tipping Platform} \textbullet{} {\footnotesize\href{https://github.com/Dnreikronos/crypto-tip}{GitHub (34 Stars)}}\\
{\footnotesize Smart contracts in Solidity (Ethereum) and Rust (Solana) for open-source funding. Integrates MetaMask and Phantom wallets.}

\vspace{2pt}
\noindent\textbf{\footnotesize givemoney.fun | Web3 Streaming Donation Platform}\\
{\footnotesize Web3 app for Twitch/Kick/YouTube streamers to receive crypto donations. Solidity and Solana smart contracts with reentrancy guards.}

\vspace{2pt}
\noindent\textbf{\footnotesize Veste AI | AI-Powered Fashion Assistant} \textbullet{} {\footnotesize\href{https://github.com/Dnreikronos/HB02-2025_braindancers}{GitHub}}\\
{\footnotesize Golang backend that uses the Google Gemini API to analyze outfits. Built at a hackathon. REST API with cloud-based processing.}

\vspace{2pt}
\noindent\textbf{\footnotesize Proof Of Learn | AI + Web3 Platform} \textbullet{} {\footnotesize\href{https://github.com/Dnreikronos/proof-of-learn}{GitHub (NearX \& ZKVerify Hackathon)}}\\
{\footnotesize Generates AI-powered learning roadmaps with on-chain incentives. Uses NEAR Protocol and Zero-Knowledge Proofs for NFT credential issuance.}

\vspace{2pt}
\noindent\textbf{\footnotesize Pattpay | Web3 Payment Gateway} \textbullet{} {\footnotesize\href{https://github.com/Dnreikronos/pattpay}{GitHub (Cypherpunk Hackathon)}}\\
{\footnotesize Subscription billing on Solana. Smart contracts handle recurring payments with sub-second finality using SPL tokens.}

\section{Technical Skills}

\vspace{2pt}
\noindent{\footnotesize
\textbf{Languages:} Go (Golang), Rust, Java, TypeScript, JavaScript, SQL, Bash\\
\textbf{Backend:} Microservices, RESTful APIs, gRPC, GraphQL, Spring Boot, NestJS, Express.js, Event-Driven Architecture\\
\textbf{Messaging:} Apache Kafka, RabbitMQ, Amazon SQS\\
\textbf{Databases:} PostgreSQL, MongoDB, Redis, Elasticsearch, MySQL, Query Optimization\\
\textbf{Infrastructure:} Docker, Kubernetes, AWS (EC2, S3, RDS, Lambda), Oracle Cloud Infrastructure (OCI), Linux\\
\textbf{DevOps:} CI/CD Pipelines, Grafana, Prometheus, ELK Stack, Performance Monitoring\\
\textbf{AI Tooling:} Claude Code, Cursor, Codex, AI-Assisted Code Review, Automated Testing\\
\textbf{Architecture:} Clean Architecture, SOLID, Design Patterns, DDD, TDD, Distributed Systems\\
\textbf{Tools:} Git, GitHub, Jira, Agile/Scrum
}

\section{Education}

\vspace{2pt}
\noindent\textbf{\footnotesize Universidade do Vale do Taquari - Univates} \hfill {\footnotesize 2021 - 2025}\\
{\footnotesize Bachelor's Degree, Computer Science}

\section{Languages}

\vspace{2pt}
\begin{center}
{\footnotesize \textbf{English} - Proficient (Professional Working Proficiency) \quad\quad \textbf{Portuguese} - Native Speaker}
\end{center}

\end{document}
